 

### 2022-02-24 doc/manuscript/tables_figures/schematic_summary.Rmd
remove DOY_g_max from summary table
#119

kable(summary_table, col.names = c("Variable", "Definition", "RP", "DP","RP", "DP"), format = "latex", booktabs = TRUE,  escape = F)%>%
  add_header_above(c(" ", " " , "SCBI" = 2, "Harvard Forest"=2)) %>%
  add_header_above(c(" ", " " , "Response to warmer spring T"=4), bold= TRUE) %>%
  column_spec(3:6, width = "1cm") %>%
  pack_rows("Timing of growth", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Daily growth rate", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual growth", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T)

>>>>

kable(summary_table, col.names = c("Variable", "Definition", "RP", "DP","RP", "DP"), format = "latex", booktabs = TRUE,  escape = F)%>%
  add_header_above(c(" ", " " , "SCBI" = 2, "Harvard Forest"=2)) %>%
  add_header_above(c(" ", " " , "Response to warmer spring T"=4), bold= TRUE) %>%
  column_spec(3:6, width = "1cm") %>%
  pack_rows("Timing of growth", 1, 4, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Daily growth rate", 5, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual growth", 6, 7, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T)
